Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-02-24 Documents/M1/realizableFermionicM1/sections/numerical.tex
Cosmetic Changes.
Some work on results.  Added figures.

@@

@@

@@

@@

@@

>>>>

To compare the accuracy of the IMEX schemes, we present results from smooth problems in streaming, absorption, and scattering dominated regimes in one spatial dimension.  
In all tests, we employ the maximum entropy closure in the low occupancy limit (i.e., the Minerbo closure).

@@

Periodic domain $D=\{x:x\in[0,1]\}$.  
The initial condition is given by
\begin{equation}
  \cJ(x,t=0)=\cH_{x}(x,t=0)=0.5+0.49\times\sin\big(2\pi\,x\big).  
\end{equation}

@@

Periodic domain $D=\{x:x\in[0,1]\}$.

@@

\subsection{Packed Beam}

Next we consider a one-dimensional test with discontinuous initial conditions.  
The computational domain is $D=\{x:x\in[-1,1]\}$, and the initial condition is obtained from a distribution function given by
\begin{equation}
  f(x,\mu)
  =\left\{
  \begin{array}{cl}
    1        & \text{if} ~ x\le x_{\mbox{\tiny D}}, ~ \mu\ge\mu_{\mbox{\tiny D}} \\
    \delta & \text{if} ~ x\le x_{\mbox{\tiny D}}, ~ \mu<   \mu_{\mbox{\tiny D}} \\
    \delta & \text{otherwise},
  \end{array}
  \right.
\end{equation}
so that $\vect{\cM}=\big(0.5\,(1+\delta),0.25\,(1-\delta)\big)^{T}$ for $x\le x_{\mbox{\tiny D}}$, and $\vect{\cM}=\big(\delta,0\big)^{T}$ for $x> x_{\mbox{\tiny D}}$.  
We let $\delta=10^{-8}$.  
\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{figures/PackedBeam_ME_CB}
    \includegraphics[width=0.5\textwidth]{figures/PackedBeam_ME_MI}
  \end{tabular}
   \caption{Packed Beam}
  \label{fig:PackedBeam}
\end{figure}

@@

The line source benchmark \citep[cf.][]{brunner_2002,garrettHauck_2013} is a challenging test for approximate transport algorithms.  
In cylindrical coordinates, it consists of an initial delta function particle distribution in radius; i.e., $f_{0}=\delta(R)/4\,\pi$.  
For $t>0$, a cylindrical radiation front propagates radially.  
Apart from capturing details of the exact transport solution, maintaining realizability ($\bcM\in\cR$ cf. Eq.~\eqref{eq:realizableSet}) of the two-moment solution is challenging.

This test is computed on a two-dimensional domain with $D=\{\vect{x}\in\bbR^{2}:x^{1}\in[0,1.25], x^{2}\in[0,1.25]\}$.  
We follow the initialization procedure in \citet{garrettHauck_2013}, and approximate the initial condition with an isotropic Gaussian distribution function
\begin{equation}
  f_{\mbox{\tiny G},0}
  =\max\Big[\,\f{1}{8\,\pi\,\sigma_{\mbox{\tiny G}}^{2}}\,e^{-R^{2}/(2\,\sigma_{\mbox{\tiny G}}^{2})},10^{-4}\,\Big],
\end{equation}
where $R=|\vect{x}|$, and we use $\sigma_{\mbox{\tiny G}}=0.03$.  
We run this test to a final time $t=1.0$.

@@

The homogeneous sphere test (e.g., \cite{smit_etal_1997}) considers of a sphere with radius $R$.  
Inside the sphere (radius $<R$), the absorption opacity $\sigma_{\Ab}$ and the equilibrium distribution function $f_{0}$ are set to constant values.  
The scattering opacity $\sigma_{\Scatt}$ is set to zero in this test (i.e., $\xi=1$).  
Outside the sphere, the absorption opacity is zero.  
The steady state solution, obtained by solving the transport equation in spherical symmetry, is given by
\begin{equation}
  f_{\mbox{\tiny A}}(r,\mu)=f_{0}\,\big(1-e^{-\chi_{0}\,s(r,\mu)}\big),
  \label{eq:distributionHomogeneousSphere}
\end{equation}
where
\begin{equation}
  s(r,\mu)
  =\left\{
  \begin{array}{lll}
    r\,\mu+R\,g(r,\mu) & \mbox{if}\quad r<R, & \mu\in[-1,+1], \\
    2\,R\,g(r,\mu) & \mbox{if}\quad r \ge R, & \mu\in[(1-(R/r)^{2})^{1/2},+1], \\
    0 & \mbox{otherwise},
  \end{array}
  \right.
\end{equation}
and $g(r,\mu)=[1-(r/R)^{2}(1-\mu^{2})]^{1/2}$.

\begin{figure}[h]
  \centering
%  \includegraphics[width=1.0\textwidth]{figures/HomogeneousSphere_Resolution_3}
  \begin{tabular}{cc}
%    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Resolution_1}
%    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Resolution_2}
  \end{tabular}
   \caption{Homogeneous sphere problem: 32$^{3}$, 48$^{3}$, and 64$^{3}$}
  \label{fig:HomogeneousSphere_Resolution}
\end{figure}
